---
title: "course prokect 1"
output:
  html_document: default
  pdf_document: default
---

## R Markdown

This is my first project with R markdown
```{r}
library(ggplot2)
library(scales)
library(Hmisc)
```

Loading and preprocessing the data with read.csv

```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile = paste0(getwd(), '/repdata%2Fdata%2Factivity.zip'), method = "curl")
unzip("repdata%2Fdata%2Factivity.zip",exdir = "data")
activityData <- data.table::fread(input = "data/activity.csv")
summary(activityData)
```

Tapply command
```{r}
stepsByDay <- tapply(activityData$steps, activityData$date, sum, na.rm=TRUE)
```

Plot step per day

```{r}
hist(stepsByDay, xlab='Total steps per day', ylab='Frequency using binwith 500', binwidth=500)
```

Mean and median steps by day function 

```{r}
#mean and median coding

stepsByDayMean <- mean(stepsByDay)
stepsByDayMedian <- median(stepsByDay)
#Mean
stepsByDayMean
#Median
stepsByDayMedian
```

Average steps by day

```{r}
averageStepsPerTimeBlock <- aggregate(x=list(meanSteps=activityData$steps), by=list(interval=activityData$interval), FUN=mean, na.rm=TRUE)
```

Plot 5 minutes interval
```{r}
ggplot(data=averageStepsPerTimeBlock, aes(x=interval, y=meanSteps)) +
  geom_line() +
  xlab("5-minute interval") +
  ylab("average number of steps taken") 
```

Average steps

```{r}
mostSteps <- which.max(averageStepsPerTimeBlock$meanSteps)
timeMostSteps <-  gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", averageStepsPerTimeBlock[mostSteps,'interval'])
```

Missing value
```{r}
numMissingValues <- length(which(is.na(activityData$steps)))
```

Data imputation

```{r}
activityDataImputed <- activityData
activityDataImputed$steps <- impute(activityData$steps, fun=mean)
```

Data imputation steps by steps and plot

```{r}
stepsByDayImputed <- tapply(activityDataImputed$steps, activityDataImputed$date, sum)
qplot(stepsByDayImputed, xlab='Total steps per day (imputated)', ylab='Frequency using binwith 500', binwidth=500)
```

Steps: mean and median

```{r}
stepsByDayMeanImputed <- mean(stepsByDayImputed)
stepsByDayMedianImputed <- median(stepsByDayImputed)
```


  
Searching differences about activity patterns between weekdays and weekends
 
  
```{r}
activityDataImputed$dateType <-  ifelse(as.POSIXlt(activityDataImputed$date)$wday %in% c(0,6), 'weekend', 'weekday')
```

Make a panel plot containing a time series plot

```{r}
averagedActivityDataImputed <- aggregate(steps ~ interval + dateType, data=activityDataImputed, mean)
ggplot(averagedActivityDataImputed, aes(interval, steps)) + 
  geom_line() + 
  facet_grid(dateType ~ .) +
  xlab("5-minute interval") + 
  ylab("avarage number of steps")
```
